Coherent optical creation of a single molecule

### 2020-12-04 paper.tex
Consistent 2pi in text

\begin{figure*}
  \includegraphics[width=\textwidth]{imgs/fig-det.pdf}
  \caption{Raman transition parameters as a function of tweezer and Raman power and detuning.
    (a) The light shift of the Raman resonance fitted to $a_P+b_P/\Delta$, where
    $a_P$ and $b_P=(\Omega_a^2-\Omega_m^2)/2$
    are tweezer power dependent background and $v'=0$ contribution
    to the light shift,
    $\Delta\equiv f_{\mathrm{PA}0} - f_{\mathrm{tweezer}}$ is the detuning from
    the PA resonance frequency $f_{\mathrm{PA}0}$.
    The $a_P$s are fitted to a model including linear and small quadratic light shift
    \todo{which assumes $\Omega_m\gg\Omega_a$} to obtain the Raman resonance frequency
    at zero tweezer power to be $f_{R0}=770.1969(2)~\mathrm{MHz}$.
    (b) Raman Rabi frequency ($\Omega_R$) fitted to $c_P+d_P/\Delta$, where
    $c_P$ and $d_P=\Omega_a\Omega_m/2$
    are tweezer power dependent background and $v'=0$ contribution.
    The detuning is calculated using the PA frequency fitted in (a).
    The $c_P$s and $d_P$s are proportional to $P^{1.29}$
    and the fit gives $c_P/P^{1.29}=-2\pi\times0.41(2)~\mathrm{kHz/mW^{1.29}}$
    and $d_P/P^{1.29}=-4\pi^2\times167(2)~\mathrm{kHz\cdot GHz/mW^{1.29}}$.
    The fitting results for (a) and (b) are shown in Table~\ref{tab:f-det:fit}.
    (c) Tweezer power dependency of $\Omega_m$ (top) and $\Omega_a$ (bottom) calculated from
    $b_P$ and $d_P$ on a log-log scale showing the $P^{0.5}$ scaling of $\Omega_m$ and
    the $P^{0.79}$ scaling of $\Omega_a$.
    \label{f-det}}
\end{figure*}
\begin{table}[ht]
  \centering
  \begin{tabular}{|c|c|c|c|}
    $P~(\mathrm{mW})$&$0.75$&$1.5$&$3.75$\\\hline
    $f_{\mathrm{PA}0}~(\mathrm{GHz})$&\multicolumn{3}{|c|}{$288711.8$}\\\hline
    $a~(\mathrm{MHz})$&$770.20452(6)$&$770.2081(1)$&$770.1943(3)$\\
    $b~(\mathrm{MHz\cdot GHz})$&$-12.46(2)$&$-24.44(3)$&$-60.66(8)$\\\hline
    $c~(\mathrm{2\pi\times kHz})$&$0.29(2)$&$0.63(4)$&$2.4(2)$\\
    $d~(\mathrm{4\pi^2\times MHz\cdot GHz})$&$0.115(4)$&$0.275(6)$&$0.95(3)$\\
  \end{tabular}
  \caption{Fitting results for Fig.~\ref{f-det}(a,b).
    \label{tab:f-det:fit}}
\end{table}

@@

We perform the experiment at various tweezer powers to extract the power dependence of $ \Omega_m $ and $ \Omega_a $, as shown in Fig.~\ref{f-det}c. $ \Omega_m $ scales with $ P^{0.5} $ as expected, and we obtain a fit value of $2\pi\times180.87(7)~\mathrm{MHz}/\sqrt{\mathrm{mW}}$.
This number is within $40~\mathrm{\%}$
of the value $2\pi\times296 ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$ calculated from theory. The scaling of $ \Omega_a $ differs from $ P^{0.5} $, which is the expected scaling from the laser intensity, due to the change in the atomic wavefunction caused by tighter confinement at higher power. For weakly interacting particles,
$\Omega_a$ scales as $P^{3/8}$.
However, due to the strong interaction between the two atoms in the $\ket{\uparrow_{\text{Na}}\downarrow_{\text{Cs}}}$ state, this approximation breaks down.
Instead, coupled-channel calculations show that the scaling
is very well approximated by $P^{0.29}$ within the range of confinement in our experiment. Thus, $ \Omega_a $ scales as $ P^{0.79} $, which fits well to our experimental result.
The fit value is $2\pi\times1.85(3)~\mathrm{MHz}/\mathrm{P^{0.79}}$. At $3.75~\mathrm{mW}$ tweezer power, we measured $ \Omega_m = 2\pi \times 348.3(3)~\mathrm{MHz}$ and $ \Omega_a = 2\pi\times 5.5(2)~\mathrm{MHz}$, resulting in a $ \Omega_m/\Omega_a$ ratio of about $ 63 $, which is close to the theory prediction of $77.7$~(Table~\ref{tab:rabi_freqs}).
Therefore, the matrix element ratio is not the cause of our lower than expected transfer efficiency.
Furthermore, we independently measure the natural linewidth of the $v'=0$ excited state to be no larger than $50~\mathrm{MHz}$ using photoassociation (PA) spectroscopy, which cannot explain the excess scattering either.
%We observe that the resonance frequency depends linearly on the tweezer power due to the differential light shift between the atomic and molecular state.
% From these measurements, we can extract a $\Omega_m$ of

%In order to calculate the ratio $\Omega_m/\Omega_a$,
%we now need to extract $ \Omega_a $.
%We do this by measuring the dependence of the Raman Rabi frequency on power and detuning.
% which depends on both $\Omega_m$ and $\Omega_a$.
%The Raman Rabi frequency shows a non-linear dependency on the tweezer power
%due to the change in the atomic wavefunction caused by
%tighter confinement at higher power, as shown in Fig.~\ref{f-det}b.

%Combined with the standard intensity factor, the Raman Rabi frequency should scale as $P^{1.29}$,
%which fits well to our experimental result, as shown in Fig.~\ref{f-det}b.
%Similar to the light shift, the detuning dependency of the Raman Rabi frequency
%is determined by a constant background component and
%a $v'=0$ component that scales as $1/\Delta$.
%The $v'=0$ component of the Raman Rabi frequency at our detuning is
%$2\pi\times1.10(2)~\mathrm{kHz\cdot mW^{-1.29}}$,
%or $2\pi \times 6.08(9)~\mathrm{kHz}$ at $3.75~\mathrm{mW}$ %tweezer power.
%Together with the $\Omega_m$ measured above, the Rabi frequency, $\Omega_a$, is
%$2\pi\times 5.5(2)~\mathrm{MHz}$.
%This gives a matrix-element ratio $\Omega_m/\Omega_a$ of $63(3)$,
%which is close to the theory prediction of $77.7$~(Table~\ref{tab:rabi_freqs}).

@@

%With the contribution of the $ v' = 0 $ state to the Raman Rabi frequency and scattering investigated,
We now consider the background effects from other states with larger single-photon detuning.
In the Raman Rabi frequency fit,
the fitted background is of opposite sign from the Raman Rabi frequency
for single-photon detunings red of the $v' = 0 $ transition.
Thus, this background reduces the Raman Rabi frequency by about $30~\mathrm{\%}$
at the current detuning.
However, this difference is not enough to explain the discrapancy of more than a factor of $10$
present in the experiment.
Due to the change in sign of the Raman Rabi frequency as a function of detuning
when crossing a resonance, the same background will increase the Raman Rabi frequency
for positive detunings from the $v' = 0$ transition.
Unfortunately, we observe additional nearby excited states
belonging to a different electronically excited state at higher frequencies
which prevent the blue side of the transition from being be usable for the Raman transition.

>>>>

\begin{figure*}
  \includegraphics[width=\textwidth]{imgs/fig-det.pdf}
  \caption{Raman transition parameters as a function of tweezer and Raman power and detuning.
    (a) The Raman resonance fitted to $a_P+b_P/\Delta$, where
    $a_P$ and $b_P=(\Omega_a^2-\Omega_m^2)/2$
    are tweezer power dependent background and $v'=0$ contribution
    to the light shift,
    $\Delta\equiv2\pi\times\paren{f_{\mathrm{PA}0} - f_{\mathrm{tweezer}}}$ is the detuning from
    the PA resonance frequency $f_{\mathrm{PA}0}$.
    The $a_P$s are fitted to a model including linear and small quadratic light shift
    \todo{which assumes $\Omega_m\gg\Omega_a$} to obtain the Raman resonance frequency
    at zero tweezer power to be $\omega_{R0}=2\pi\times770.1969(2)~\mathrm{MHz}$.
    (b) Raman Rabi frequency ($\Omega_R$) fitted to $c_P+d_P/\Delta$, where
    $c_P$ and $d_P=\Omega_a\Omega_m/2$
    are tweezer power dependent background and $v'=0$ contribution.
    The detuning is calculated using the PA frequency fitted in (a).
    The $c_P$s and $d_P$s are proportional to $P^{1.29}$
    and the fit gives $c_P/P^{1.29}=-2\pi\times0.41(2)~\mathrm{kHz/mW^{1.29}}$
    and $d_P/P^{1.29}=-4\pi^2\times167(2)~\mathrm{kHz\cdot GHz/mW^{1.29}}$.
    The fitting results for (a) and (b) are shown in Table~\ref{tab:f-det:fit}.
    (c) Tweezer power dependency of $\Omega_m$ (top) and $\Omega_a$ (bottom) calculated from
    $b_P$ and $d_P$ on a log-log scale showing the $P^{0.5}$ scaling of $\Omega_m$ and
    the $P^{0.79}$ scaling of $\Omega_a$.
    \label{f-det}}
\end{figure*}
\begin{table}[ht]
  \centering
  \begin{tabular}{|c|c|c|c|}
    $P~(\mathrm{mW})$&$0.75$&$1.5$&$3.75$\\\hline
    $f_{\mathrm{PA}0}~(\mathrm{GHz})$&\multicolumn{3}{|c|}{$288711.8$}\\\hline
    $a~(\mathrm{2\pi\times MHz})$&$770.20452(6)$&$770.2081(1)$&$770.1943(3)$\\
    $b~(\mathrm{4\pi^2\times MHz\cdot GHz})$&$-12.46(2)$&$-24.44(3)$&$-60.66(8)$\\\hline
    $c~(\mathrm{2\pi\times kHz})$&$0.29(2)$&$0.63(4)$&$2.4(2)$\\
    $d~(\mathrm{4\pi^2\times MHz\cdot GHz})$&$0.115(4)$&$0.275(6)$&$0.95(3)$\\
  \end{tabular}
  \caption{Fitting results for Fig.~\ref{f-det}(a,b).
    \label{tab:f-det:fit}}
\end{table}

@@

We perform the experiment at various tweezer powers to extract the power dependence of $ \Omega_m $ and $ \Omega_a $, as shown in Fig.~\ref{f-det}c. $ \Omega_m $ scales with $ P^{0.5} $ as expected, and we obtain a fit value of $2\pi\times180.87(7)~\mathrm{MHz}/\sqrt{\mathrm{mW}}$.
This number is within $40~\mathrm{\%}$
of the value $2\pi\times296 ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$ calculated from theory. The scaling of $ \Omega_a $ differs from $ P^{0.5} $, which is the expected scaling from the laser intensity, due to the change in the atomic wavefunction caused by tighter confinement at higher power. For weakly interacting particles,
$\Omega_a$ scales as $P^{3/8}$.
However, due to the strong interaction between the two atoms in the $\ket{\uparrow_{\text{Na}}\downarrow_{\text{Cs}}}$ state, this approximation breaks down.
Instead, coupled-channel calculations show that the scaling
is very well approximated by $P^{0.29}$ within the range of confinement in our experiment. Thus, $ \Omega_a $ scales as $ P^{0.79} $, which fits well to our experimental result.
The fit value is $2\pi\times1.85(3)~\mathrm{MHz}/\mathrm{P^{0.79}}$. At $3.75~\mathrm{mW}$ tweezer power, we measured $ \Omega_m = 2\pi \times 348.3(3)~\mathrm{MHz}$ and $ \Omega_a = 2\pi\times 5.5(2)~\mathrm{MHz}$, resulting in a $ \Omega_m/\Omega_a$ ratio of about $ 63 $, which is close to the theory prediction of $77.7$~(Table~\ref{tab:rabi_freqs}).
Therefore, the matrix element ratio is not the cause of our lower than expected transfer efficiency.
Furthermore, we independently measure the natural linewidth of the $v'=0$ excited state to be no larger than $50~\mathrm{MHz}$ using photoassociation (PA) spectroscopy, which cannot explain the excess scattering either.
% We observe that the resonance frequency depends linearly on the tweezer power due to the differential light shift between the atomic and molecular state.
% From these measurements, we can extract a $\Omega_m$ of

% In order to calculate the ratio $\Omega_m/\Omega_a$,
% we now need to extract $ \Omega_a $.
% We do this by measuring the dependence of the Raman Rabi frequency on power and detuning.
% which depends on both $\Omega_m$ and $\Omega_a$.
% The Raman Rabi frequency shows a non-linear dependency on the tweezer power
% due to the change in the atomic wavefunction caused by
% tighter confinement at higher power, as shown in Fig.~\ref{f-det}b.

% Combined with the standard intensity factor, the Raman Rabi frequency should scale as $P^{1.29}$,
% which fits well to our experimental result, as shown in Fig.~\ref{f-det}b.
% Similar to the light shift, the detuning dependency of the Raman Rabi frequency
% is determined by a constant background component and
% a $v'=0$ component that scales as $1/\Delta$.
% The $v'=0$ component of the Raman Rabi frequency at our detuning is
% $2\pi\times1.10(2)~\mathrm{kHz\cdot mW^{-1.29}}$,
% or $2\pi \times 6.08(9)~\mathrm{kHz}$ at $3.75~\mathrm{mW}$ %tweezer power.
% Together with the $\Omega_m$ measured above, the Rabi frequency, $\Omega_a$, is
% $2\pi\times 5.5(2)~\mathrm{MHz}$.
% This gives a matrix-element ratio $\Omega_m/\Omega_a$ of $63(3)$,
% which is close to the theory prediction of $77.7$~(Table~\ref{tab:rabi_freqs}).

@@

% With the contribution of the $ v' = 0 $ state to the Raman Rabi frequency and scattering investigated,
We now consider the background effects from other states with larger single-photon detuning.
In the Raman Rabi frequency fit,
the fitted background is of opposite sign from the Raman Rabi frequency
for single-photon detunings red of the $v' = 0 $ transition.
Thus, this background reduces the Raman Rabi frequency by about $30~\mathrm{\%}$
at the current detuning.
However, this difference is not enough to explain the discrapancy of more than a factor of $10$
present in the experiment.
Due to the change in sign of the Raman Rabi frequency as a function of detuning
when crossing a resonance, the same background will increase the Raman Rabi frequency
for positive detunings from the $v' = 0$ transition.
Unfortunately, we observe additional nearby excited states
belonging to a different electronically excited state at higher frequencies
which prevent the blue side of the transition from being be usable for the Raman transition.
